---
title: "wordle"
author: "Claire Brandes"
date: "2024-02-21"
output: html_document
---

# Wordle Challenge: Applied Data Analysis 2024

## Step 1

Create custom function called load_dictionary() that takes a single argument, "filename", that can be sued to read in either of the two data files downloaded.

```{r}
load_dictionary <- function(filename) {
  library(readr)
  f <- filename
  return(read_tsv(f, col_names = TRUE))
}
```

Use the load_dictionary() function to create two variables, solution_list and valid_list, that, respectively contain vectors of possible solution words and valid words to guess.

```{r}
valid_list <- load_dictionary("https://raw.githubusercontent.com/clairebran/exercise-04/main/collins-scrabble-words-2019.txt")

solution_list <- load_dictionary("https://raw.githubusercontent.com/clairebran/exercise-04/main/google-10000-english-usa-no-swears.txt")
```

## Step 2

Winnow variable solution_list to only include words that are included in valid_list. The solution list now has only 8,336 words when before it had 9,884. 

```{r}
library(dplyr)
solution_list <- inner_join(valid_list, solution_list, by = join_by(words))
```

## Step 3

Write custom function called pick_solution() that (1) removes all words from solution_list that are not 5 letters in length, (2) randomly chooses a single word from those that remain, and (3) splits that word into a vector of single-character elements. 

```{r}
pick_solution <- function(solution_list) {
  solution_list$five_words <- nchar(solution_list$words) == 5 
  solution_list <- subset(solution_list, five_words == "TRUE", words)
  answer <- sample(solution_list$words, 1)
  answer <- unlist(strsplit(answer, split = ""))
  return(answer)
}
```

Run function and assign the result to a variable called solution:

```{r}
solution <- unlist(pick_solution(solution_list))
```

## Step 4

Create function called play_wordle() that takes three arguments: (1) the answer to the puzzle, (2) a list of valid guesses, and (3) a value for number of guesses. 

```{r}
play_wordle <- function(solution, valid_list, num_guesses = 6) {
  library(stringr)
  
  welcome_message <- "Welcome to Wordle! Guess the solution in 6 tries. Each guess must be a valid 5-letter word. A letter will be replaced with * if it is in the word and in the correct spot. A letter will be replaced with + if it is in the word but in the incorrect spot. A letter will be replaced with - if it is not anywhere in the word."
  
  print(welcome_message, quote = FALSE)
  for (i in 1:num_guesses) {
  guess <- readline("Enter your 5-letter guess here, then press enter: ")
  guess <- unlist(strsplit(guess, split = ""))
  guess <- toupper(guess)
  print("Letters not yet guessed: ")
  letters_left <- (setdiff(LETTERS, guess))
  print(letters_left)
  print(evaluate_guess(guess, solution))
  }
}
```

Create function called evaluate_guess() that provides feedback based on guess input. 

```{r}
evaluate_guess <- function(guess, solution) {
  if (setequal(guess[1], solution[1])==TRUE) {
    guess <- str_replace(guess, guess[1], "*")
    cat(guess, "\nNice job!")
  } else {
    if (any(solution==guess[1])==TRUE) {
      guess <- str_replace(guess, guess[1], "+")
      cat(guess, "\nSo close! Try moving your letters around")
    } else {
      guess <- str_replace(guess, guess[1], "-")
      cat(guess, "\nUh oh! Try again.")
    }
  }
  if (setequal(guess[2], solution[2])==TRUE) {
    guess <- str_replace(guess, guess[2], "*")
    feedback <- cat(guess, "\nNice job!") 
  } else {
    if (any(solution==guess[2])==TRUE) {
      guess <- str_replace(guess, guess[2], "+")
      cat(guess, "\nSo close! Try moving your letters around")
    } else {
      guess <- str_replace(guess, guess[2], "-")
      cat(guess, "\nUh oh! Try again.")
    }
  }
  if (setequal(guess[3], solution[3])==TRUE) {
    guess <- str_replace(guess, guess[3], "*")
    cat(guess, "\nNice job!") 
  } else {
    if (any(solution==guess[3])==TRUE) {
      guess <- str_replace(guess, guess[3], "+")
      cat(guess, "\nSo close! Try moving your letters around")
    } else {
      guess <- str_replace(guess, guess[3], "-")
      cat(guess, "\nUh oh! Try again.")
    }
  }
  if (setequal(guess[4], solution[4])==TRUE) {
    guess <- str_replace(guess, guess[4], "*")
    cat(guess, "\nNice job!") 
  } else {
    if (any(solution==guess[4])==TRUE) {
      guess <- str_replace(guess, guess[4], "+")
      cat(guess, "\nSo close! Try moving your letters around")
    } else {
      guess <- str_replace(guess, guess[4], "-")
      cat(guess, "\nUh oh! Try again.")
    }
  }
  if (setequal(guess[5], solution[5])==TRUE) {
    guess <- str_replace(guess, guess[5], "*")
    cat(guess, "\nNice job!") 
  } else {
    if (any(solution==guess[5])==TRUE) {
      guess <- str_replace(guess, guess[5], "+")
      cat(guess, "\nSo close! Try moving your letters around")
    } else {
      guess <- str_replace(guess, guess[5], "-")
      cat(guess, "\nUh oh! Try again.")
    }
  }
  if (setequal(guess,solution)==TRUE) {
    cat(guess, "\nWinner Winner! You're a Wordle pro!")
  } else {
    cat(guess, "\nTough luck! Try again next time.")
  }
}
```

